### 2018-12-01 pilot_manuscript.Rmd
added the apa table elements

The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a percentage of their occurrence and their valence. Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated and this process was repeated for each of the foundations. This procedure created five percentages that were included as the dependent variable for the following analyses. 
```{r stem_text, eval=TRUE, include=FALSE}

@@

```{r descriptives, include = FALSE}
#summarize the dataset so that you have the total and percent for each foundation

#report descriptive statistics of the foundations

#note that a big problem is the valence of the words 
```

@@

#calculate d
harm_d = d.ind.t(m1 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
                 sd1 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T),
                 sd2 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
                 n1 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"]),
                 n2 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"]),
                 a = .05)

#put in the numbers
tableprint[1, ] = c("Harm", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
                    harm_d$d)

@@

On September 27, the committee questioned Dr. Ford before commencing a second round of questioning for Judge Kavanaugh [@CITE_CONGRESSIONAL_RECORD]. During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh. According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television. This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States. On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor. Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved. The investigation concluded with no significant findings. The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@CITE_CONGRESSIONAL_RECORD].

>>>>

The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with their valence and a percentage of their occurrence. Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated, and this process was repeated for each of the foundations. This procedure created five percentages that were included as the dependent variable for the following analyses. 
```{r stem_text, eval=TRUE, include=FALSE}

@@

```{r descriptives, include = FALSE}
#summarize the dataset so that you have the total and percent for each foundation
summary(harm_final_data)
summary(fair_final_data)
summary(ingroup_final_data)
summary(authority_final_data)
summary(purity_final_data)
#report descriptive statistics of the foundations
mean(harm_final_data$valence)
sd(harm_final_data$valence)
mean(fair_final_data$valence)
sd(fair_final_data$valence)
mean(ingroup_final_data$valence)
sd(ingroup_final_data$valence)
mean(authority_final_data$valence)
sd(authority_final_data$valence)
mean(purity_final_data$valence)
sd(purity_final_data$valence)
#note that a big problem is the valence of the words 
```

@@

#calculate d
#harm
harm_d = d.ind.t(m1 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
                 sd1 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T),
                 sd2 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
                 n1 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"]),
                 n2 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"]),
                 a = .05)

#fair
fair_d = d.ind.t(m1 = mean(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"], na.rm = T),
                 sd1 = sd(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"], na.rm = T),
                 sd2 = sd(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"], na.rm = T),
                 n1 = length(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"]),
                 n2 = length(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"]),
                 a = .05)

#ingroup
ingroup_d = d.ind.t(m1 = mean(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"], na.rm = T),
                 sd1 = sd(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"], na.rm = T),
                 sd2 = sd(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"], na.rm = T),
                 n1 = length(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"]),
                 n2 = length(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"]),
                 a = .05)

#authority
authority_d = d.ind.t(m1 = mean(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"], na.rm = T),
                 sd1 = sd(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"], na.rm = T),
                 sd2 = sd(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"], na.rm = T),
                 n1 = length(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"]),
                 n2 = length(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"]),
                 a = .05)

#purity
purity_d = d.ind.t(m1 = mean(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"], na.rm = T),
                 sd1 = sd(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"], na.rm = T),
                 sd2 = sd(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"], na.rm = T),
                 n1 = length(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"]),
                 n2 = length(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"]),
                 a = .05)

#put in the numbers
tableprint[1, ] = c("Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
                    harm_d$d)
tableprint[2, ] = c("Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1, 
                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
                    fair_d$d)
tableprint[3, ] = c("Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1, 
                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
                    ingroup_d$d)
tableprint[4, ] = c("Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1, 
                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
                    authority_d$d)
tableprint[5, ] = c("Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1, 
                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
                    purity_d$d)

@@

On September 27, the committee questioned Dr. Ford before commencing a second round of questioning for Judge Kavanaugh [@CITE_CONGRESSIONAL_RECORD]. During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh. According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television [@CITE_NIELSEN]. This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States. On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor. Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved. The investigation concluded with no significant findings. The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@CITE_CONGRESSIONAL_RECORD].
